Review questions list

### 2020-10-10 docs/revision/review.tex
fix::16 - update::18

\textcolor{red}{Following CK comment: The argument will be dropped}

@@

\item \textbf{-HARD-} The authors wrote, "The most important contribution of this research is the use of
the GAN phase, where the available data is expanded to be
used in the training phase". Why use a Generative adversarial network? What would be the advantages and disadvantages of a GAN approach over other possible data generators, such as evolutionary mutation functions? The authors should provide a comparison methodology and discuss differences between GAN and other data generators. \\
\textcolor{darkgreen}{ANSWER: } To be investigated in future research.\\ \textcolor{red}{CK comment: We can talk about this in here and maybe in paper. I am not sure he is requesting experiments. We can avoid experiments by adding it to future works.}

@@

>>>>

\textcolor{red}{Following CK comment: The argument will be dropped}
\textcolor{darkgreen}{AZ: The argument is dropped; commented out in the latex file 'paper.tex' line 860}

\fixed{}

@@

\item \textbf{-HARD-} The authors wrote, "The most important contribution of this research is the use of
the GAN phase, where the available data is expanded to be
used in the training phase". Why use a Generative adversarial network? What would be the advantages and disadvantages of a GAN approach over other possible data generators, such as evolutionary mutation functions? The authors should provide a comparison methodology and discuss differences between GAN and other data generators. \\
\textcolor{darkgreen}{ANSWER: } To be investigated in future research.\\ \textcolor{red}{CK comment: We can talk about this in here and maybe in paper. I am not sure he is requesting experiments. We can avoid experiments by adding it to future works.} \\
\textcolor{blue}{AZ: We already mentioned and gave references demonstrating the effectiveness and flexibility of GANs. As they are becoming very common method in data augmentation, we have investigated its power to solve the problem at hand. Furthermore, our study was not comparative in nature with regards to data augmentation methods. \\
Concerning other methods, more experiments , which are beyond the scope of this study, will be conducted to select the the optimal technique.}

@@

\fixed{}
